\documentclass{resume}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \usepackage{fontawesome}
\usepackage{fontawesome5}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=blue
}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\name{\;\;\;\;\;\;\;\;\;\;\;Vladislav Buravko} % Your name
\address{Moscow, Russia} % Your address
\address{
    \faGithub \enspace \href{https://github.com/UniverTime}{UniverTime}
}   


\begin{document}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Moscow Institute of Physics and Technology}{Moscow, Russia}
      {Bachelor of applied mathematics and physics;  GPA: 7.30}{Sep 2021 -- Present}
      \resumeItemListStart
      \medskip
      \resumeItem{Relevant additional courses} {STM32, C++, ILab (Intel): lecturer - Dedinsky I.R., Huawei (ISP RAS): lecturer - Dedinsky I.R.}
      \resumeItemListEnd
      %\bigskip
      
  \resumeSubHeadingListEnd

\section{Skills}
 \resumeSubHeadingListStart
    \item{
    \textbf{Languages}{: Russian (Native), English (Upper-Intermediate), Deutsch (Elementary)}
    }
    \smallskip
   \item{
     \textbf{Programming languages}{: C, C++, Assembly, Bash, Python}
   }
   \smallskip
   \item{\textbf{Technologies}{: Git, Make, Graphviz, GDB, Markdown, HTML, GitHub Actions}
   }
   \smallskip
   \item{\textbf{Hardware}{: STM32, Raspberry Pi}
   }
 \resumeSubHeadingListEnd


\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/UniverTime/Language}{Language}}
      {A completely new programming language written from scratch to create an assembly file and run programs on a virtual processor. The analysis of the written code takes place using a multi-level recursive descent.}
      \bigskip
    \resumeSubItem{\href{https://github.com/UniverTime/CPU}{CPU}}
    {My own virtual processor running on its own assembler. It has a single contiguous memory zone for the stack, video memory and executable code.}
    \bigskip
    \resumeSubItem{\href{https://github.com/UniverTime/Akinator}{Akinator - MIPT assistant}}
      {A cute creature that won't let you get bored. You can sort all your acquaintances and friends into different categories. The information is stored as a binary tree. It also has the ability to embed a secret personalized branch using a secret word-code. The secret branch is hashed and inaccessible to ordinary users.}
      \bigskip
    \resumeSubItem{\href{https://github.com/UniverTime/Differentiator}{Differentiator}}
      {If it is necessary to take the derivative of a huge and incomprehensible function to your mind. You need to familiarize yourself with this project. In addition, a unique scientific article is created there every time, about how this happens.}
      \bigskip
    \resumeSubItem{\href{https://github.com/UniverTime/Parallelization}{Parallelization using pthread API}}
      {Some program can be speed up using multiple threads of execution. A good example of this speed up can be a calculation of integral using the Monte Carlo method.}
      \bigskip
    \resumeSubItem{\href{https://github.com/UniverTime/STM32}{STM32}}
      {A course on working with hardware and interaction at the lowest level. Without any libraries. Only registers, C, assembler and nothing else.}
      \bigskip
      \resumeSubItem{\href{https://github.com/UniverTime}{The full list is on my github}}
      {}
      
  \resumeSubHeadingListEnd
\end{document}